humanCdGF_predict_cfu

### 2016-11-07 code/HumanCdGF_predict_cfu.Rmd
fix partial plots to work with rfe output

```{r setup environment}
pack_used <- c('randomForest','miscTools','tidyr','ggplot2','dplyr', 'pROC', 'knitr', 'cowplot', 'caret')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

@@

rfe_ctrl <- rfeControl(functions = rfRFE,
                   method = "repeatedcv",
                   repeats = 10,
                   verbose = FALSE)
subsets <- c(1:5, c(seq(10, 70, 10)))
set.seed(seed)
rf_model <- rfe(cfu_shared_colonized.df[ , -1], cfu_shared_colonized.df$log_cfu_med,
                 sizes = subsets,
                 rfeControl = rfe_ctrl)
rf_test <- train(cfu_shared_colonized.df[ , importance_final], cfu_shared_colonized.df$log_cfu_med,
                 method = 'rf', importance = T)
partialPlot(rf_test$finalModel, cfu_shared_colonized.df, 'Otu000004')

xrf_test <- randomForest(log_cfu_med ~ ., data = cfu_shared_colonized.df[ , 1:30],
                     importance = TRUE, ntree = 100)

importance_final <- predictors(rf_model)

@@

om_import_otus <- data.frame(om_import_otus[ , -1], row.names = om_import_otus$otu)
colnames(om_import_otus) <- seq(ncol(om_import_otus))
om_otu_rank <- apply(om_import_otus, 2, function(x) rank(x, na.last = F))
om_raw_rank <- apply(om_otu_rank, 1, function(x) sum(x, na.rm = T))
med_otu_importance_om <- data.frame(otu = names(om_raw_rank),
                                 importance = om_raw_rank)

@@

color <- sapply(1:length(unique(partial_df$cage_id)), 
                           function(n){
                             set.seed(n+10) # add modify to generate distinct colors
                             rgb(sample(c(0:255), 1),sample(c(0:255), 1),
                                 sample(c(0:255), 1), maxColorValue = 255)
                             })
partialPlot(rf_n_features, top_colonized_df, x.var=rownames(importance_om)[otu])
layout(matrix(c(1:4), ncol=2, byrow=TRUE))
for(otu in seq_along(importance_om$tax)){
    partialPlot(rf_n_features, top_colonized_df, x.var=rownames(importance_om)[otu],
                xlab='', main=paste(importance_om$tax_label[otu]))
    par(new = T)
    plot(y = top_colonized_df[ , 'log_cfu_med'],
         x = top_colonized_df[ , rownames(importance_om)[otu]], 
         pch = 21, bg = 'gray', xlab = NA, ylab = NA, axes = F)
    axis(side = 4)
    mtext(side = 4, line = 3, 'Log10 CFU')
    if(length(features_cor[[otu]]) > 1){
    mtext(side = 1, line = 3, cex = 0.6,
          paste('Bacteria removed in preprocessing due to correlation to this OTU:\n',
                paste(get_tax(row_list = features_cor[[otu]])$tax_label, collapse = ',')))
    }
# To color points by mouse - Change pch to 21 and un-comment following lines
  lapply(seq_along(unique(partial_df$cage_id)), function(m){
    mouse <- unique(partial_df$cage_id)[m]
    points(y = partial_df[partial_df$cage_id %in% mouse, 'log_cfu_med'],
           x = partial_df[partial_df$cage_id %in% mouse , rownames(importance_om)[otu]], 
           pch = 21, cex = 2, bg = color[m], xlab = NA, ylab = NA, axes = F)
  })
}
```

>>>>

```{r setup environment}
pack_used <- c('randomForest','tidyr','ggplot2','plyr', 'dplyr', 'caret')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

@@

rfe_ctrl <- rfeControl(functions = rfRFE,
                   method = "repeatedcv",
                   repeats = 10,
                   verbose = FALSE)
subsets <- c(1:5, c(seq(10, 70, 10)))
set.seed(seed)
rf_model <- rfe(cfu_shared_colonized.df[ , -1], cfu_shared_colonized.df$log_cfu_med,
                 sizes = subsets,
                 rfeControl = rfe_ctrl)
top_important_OTU <- predictors(rf_model)

@@

om_import_otus <- data.frame(om_import_otus[ , -1], row.names = om_import_otus$otu)
colnames(om_import_otus) <- seq(ncol(om_import_otus))
om_otu_rank <- apply(om_import_otus, 2, function(x) rank(x, na.last = F))
om_raw_rank <- sort(apply(om_otu_rank, 1, function(x) sum(x, na.rm = T)), decreasing = T)
med_otu_importance_om <- data.frame(otu = names(om_raw_rank),
                                 importance = om_raw_rank)

@@

color <- sapply(1:length(unique(partial_df$cage_id)), 
                           function(n){
                             set.seed(n+10) # add modify to generate distinct colors
                             rgb(sample(c(0:255), 1),sample(c(0:255), 1),
                                 sample(c(0:255), 1), maxColorValue = 255)
                             })

layout(matrix(c(1:16), ncol=4, byrow=TRUE))
for(otu in seq_along(importance_om$tax)){
    partialPlot(rf_n_features, data.frame(cfu_shared_colonized.df), x.var=rownames(importance_om)[otu],
                xlab='', main=paste(importance_om$tax_label[otu]))
    par(new = T)
    plot(y = partial_df[ , 'log_cfu_med'],
         x = partial_df[ , rownames(importance_om)[otu]], 
         pch = NA, bg = 'gray', xlab = NA, ylab = NA, axes = F)
    axis(side = 4)
    mtext(side = 4, line = 3, 'Log10 CFU')
    if(length(features_cor[[otu]]) > 1){
    mtext(side = 1, line = 3, cex = 0.6,
          paste('Bacteria removed in preprocessing due to correlation to this OTU:\n',
                paste(get_tax(row_list = features_cor[[otu]])$tax_label, collapse = ',')))
    }
# To color points by mouse - Change pch to 21 and un-comment following lines
  lapply(seq_along(unique(partial_df$cage_id)), function(m){
    mouse <- unique(partial_df$cage_id)[m]
    points(y = partial_df[partial_df$cage_id %in% mouse, 'log_cfu_med'],
           x = partial_df[partial_df$cage_id %in% mouse , rownames(importance_om)[otu]], 
           pch = 21, cex = 2, bg = color[m], xlab = NA, ylab = NA, axes = F)
  })
}
```
